Stability concerns in random matrices

### 2018-03-23 random_matrix_stability.Rmd
Work on figure

```{r, echo = FALSE}
library(knitr);
dat  <- read.table(file = "full_data.csv", header = TRUE, sep = ",");
dat  <- cbind(dat, (dat[,3] - dat[,4]) + dat[,5]);
rownames(dat) <- NULL;
colnames(dat) <- c("Species ($\\{S}$)", "Unstable", "Stable", "Stabilised", 
                   "Destabilised", "Stable ($\\{Var(gamma)}$)")
```

@@

```{r, echo = FALSE}
kable(dat);
```

@@

| Species ($S$) | Unstable  | Stable   | Stabilised   | Destabilised | Stable ($Var(\gamma)$) |
|---------------|-----------|----------|--------------|--------------|------------------------|
| 2             | 73788328  | 23789690 | 1210228      | 1211754      | 23788164               |
| 3             | 87850079  | 9449619  | 1613996      | 1086306      | 9977309                |
| 4             | 94978045  | 3153446  | 1224826      | 643683       | 3734589                |
| 5             | 98173012  | 878074   | 662411       | 286503       | 1253982                |
| 6             | 99415760  | 204708   | 279491       | 100041       | 384158                 |
| 7             | 99837320  | 39806    | 95472        | 27402        | 107876                 |
| 8             | 99959849  | 6356     | 27660        | 6135         | 27881                  |
| 9             | 99991252  | 887      | 6693         | 1168         | 6412                   |
| 10            | 99998284  | 106      | 1439         | 171          | 1374                   |
| 11            | 99999719  | 10       | 255          | 16           | 249                    |
| 12            | 99999951  | 0        | 46           | 3            | 43                     |
| 13            | 99999994  | 0        | 5            | 1            | 4                      |
| 14            | 99999998  | 0        | 2            | 0            | 2                      |
| 15            | 100000000 | 0        | 0            | 0            | 0                      |

@@

@@

```{r, echo = TRUE, eval = TRUE}
par(mar = c(5, 5, 2, 1));
y1 <- stabilised / (stable + stabilised);
plot(x = gen_var[,1], y = y1, type = "b", lwd = 2, ylim = c(0, 1),
     xlab = "Species number", ylab = "Pr stable due to Var(gen)",
     cex.axis = 1.5, cex.lab = 1.5, lty = "solid");
```

>>>>

```{r, echo = FALSE}
library(knitr);
dat  <- read.table(file = "mat_dat.csv", header = TRUE, sep = ",");
dat  <- cbind(dat, (dat[,3] - dat[,5]) + dat[,4]);
rownames(dat) <- NULL;
colnames(dat) <- c("Species (S)", "Unstable", "Stable", "Stabilised", 
                   "Destabilised", "Stable ($\\ Var(\u03b3)$ )")
```

@@

```{r, echo = FALSE, caption = "Stability results from 100 million simulations of random interaction matrices for 2-15 species (S). Columns 2 and 3 report the number of stable and unstable communities in the absence of variation in species generation time (all $\\u03b3 = 1$). Columns 4 and 5 report the number of unstable communities stabilised or stable communities destabilised by $\\ Var(\u03b3)$, respectively. Column 6 reports the total number of communities that are stable given $\\ Var(\u03b3)$ (compare to column 3)."}
kable(dat);
```

@@

@@

```{r, echo = FALSE}
bar_dat                      <- t(cbind(dat[,3], dat[,6]));
log_bar_dat                  <- log(bar_dat);
log_bar_dat[log_bar_dat < 0] <- 0;
barplot(log_bar_dat, beside = TRUE, col = c("grey60", "grey80"),
        names.arg = dat[,1], ylim = c(0, 25), xlab = "Species number (S)",
        ylab = "Ln number of stable communities", cex.lab = 1.25, 
        cex.axis = 1.25, xlim = c(1, 42));
legend("topleft", c("\u03b3 = 1", "\u03b3 = [1, 1000]"), pch=15, 
       col=c("grey60","grey80"), cex = 1.5);
box(lwd = 2);
par(new = TRUE);
y1     <- dat[,4] / (dat[,3] + dat[,4]);
x1     <- 2:15;
x1_adj <- c(0.27, 0.25, 0.23, 0.21, 0.21, 0.20, 0.19, 0.18, 0.17, 0.16, 0.15,
            0.14, 0.13, 0.12);
plot(x = x1 + x1_adj, y = y1, xaxt = "n", yaxt = "n", lwd = 2, ylim = c(0, 1),
     xlab = "", ylab = "", type = "b", xlim = c(2, 15));

#plot(x = gen_var[,1], y = y1, type = "b", lwd = 2, ylim = c(0, 1),
#     ylab = "Pr. stable due to Var(\u03b3)",
#     cex.axis = 1.5, cex.lab = 1.5, lty = "solid");
```

@@

```{r, echo = TRUE, eval = TRUE}
par(mar = c(5, 5, 2, 1));
y1 <- stabilised / (stable + stabilised);
plot(x = gen_var[,1], y = y1, type = "b", lwd = 2, ylim = c(0, 1),
     xlab = "Species number", ylab = "Pr stable due to Var(gen)",
     cex.axis = 1.5, cex.lab = 1.5, lty = "solid");
print(stabilised);
print(stable);
print(y1);
```
